---
title: "week11-scholar"
author: "Mathi Manavalan"
date: "4/1/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Studio API Code
Setting the working directory is not necessary for an RMarkdown file.

## Libraries
Importing the libraries necessary for the data importing, cleaning, and analyzing.
```{r libraries, message=FALSE}
library(tidyverse)
library(rvest)
```

## Data Import and Cleaning
Here, I am web-scraping some data from Dr. Yuhong Jiang's Google Scholar page.
```{r}
papers <- read_html("https://scholar.google.com/citations?user=ZqlRcM8AAAAJ&hl=en&oi=ao")

titleNodes <- html_nodes(papers, ".gsc_a_at")
titleText <- html_text(titleNodes)

authorNodes <- html_nodes(papers, ".gsc_a_at+ .gs_gray")
authorText <- html_text(authorNodes)

yearNodes <- html_nodes(papers, ".gsc_a_hc")
yearText <- html_text(yearNodes)

countNodes <- html_nodes(papers, ".gsc_a_ac")
countText <- html_text(countNodes)

profile_tbl <- cbind(titleText, authorText, yearText, countText) %>% 
  as_tibble() %>% 
  mutate(countText = as.numeric(countText), yearText = as.numeric(yearText))

```

## Analysis

```{r}

sum <- summary(lm(profile_tbl$countText ~ profile_tbl$yearText))

```
The correlation between year and count is `r sum$coefficients[2,1]`. 

## Visualization

```{r, message=FALSE, include=TRUE}

plot <- ggplot(profile_tbl, aes(x=yearText, y= countText)) + 
  geom_jitter() +
  labs(x = "Year of Publication", y = "Number of Citations") +
  geom_smooth(method = "lm", se = FALSE)
plot

```
The above plot displays the relationship between the year of publication and the number of citations of some of Dr. Yuhong Jiang's publications. The plot also includes a linear regression line, modeling the relationship between the two variables linearly. 



