---
title: "week11-twitter"
author: "Mathi Manavalan"
date: "3/31/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Studio API Code
Setting the working directory is not necessary for an RMarkdown file.

## Libraries
Importing the libraries necessary for the data importing, cleaning, and analyzing.
```{r libraries, message=FALSE}
library(twitteR)
library(tidyverse)

```

## Data Import and Cleaning

```{r keys,echo=FALSE, message=FALSE, include=TRUE}

api <- "rN5sTV6MAEHLVGwLfL2GeVd7J"
secretKey <- "uM6NZknlicOfcePx5wu0bkYGZ1rne28QyOSnmttH8NW4af86P8"
token <- "1244697675271815168-WkDkHPWpYhAXIKoRq6JprQvFnB82uk"
secretToken <- "ubSRkij4Uyfx0L2jbrrDsAwGSyUBHIOZ5EapKsCggwtFx"

```
The keys inputted into the function below are the keys found for my particular app through my Twitter developer account.

```{r, message=FALSE}
setup_twitter_oauth(api, secretKey, token, secretToken)

tweets <- searchTwitter("#rstats", 1000)
tweets_clean <- strip_retweets(tweets)
tweets_tbl <- twListToDF(tweets_clean) %>% 
  select(screenName, text, favoriteCount, retweetCount)
  

```

## Analysis

```{r}

plot1sum <- summary(lm(tweets_tbl$retweetCount ~ str_length(tweets_tbl$text)))
plot1sum

```

The above statistical test creates a linear model between the number of characters in a tweet and how many times that tweet was retweeted.

```{r}

plot2sum <- summary(lm(tweets_tbl$favoriteCount ~ str_length(tweets_tbl$text)))
plot2sum

```

The above statistical test creates a linear model between the number of characters in a tweet and how many times that tweet was liked/favorited.

## Visualization

```{r, message=FALSE, include=TRUE}
plot1 <- ggplot(tweets_tbl, aes(x=str_length(text), y= retweetCount)) + 
  geom_jitter() +
  labs(x = "Number of Characters in Tweet", y = "Number of Retweets") +
  geom_smooth(method = "lm", se = FALSE)
plot1

```

The above plot displays the relationship between the number of characters in a tweet (on the x-axis) and how many times that tweet was retweeted (on the y-axis) as a scatterplot. The plot also includes a linear regression line between the two variables.

```{r, message=FALSE, include=TRUE}
plot2 <- ggplot(tweets_tbl, aes(x=str_length(text), y= favoriteCount)) + 
  geom_jitter() +
  labs(x = "Character length of Tweet", y = "Number of Likes/Favorites") +
  geom_smooth(method = "lm", se = FALSE)
plot2

```
The above plot displays the relationship between the number of characters in a tweet (on the x-axis) and how many times that tweet was 'liked' or 'favorited' (on the y-axis) as a scatterplot. The plot also includes a linear regression line between the two variables.

